---
title: "My title"
author: Diana Liu
thanks: "Code and data are available at: https://github.com/Diana-Guanzhi-Liu/Term-Paper-1."
date: 25 January 2024
abstract: "We examine marriage licenses obtained in the city of Toronto in the year 2023 by months."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(opendatatoronto)
library(dplyr)
library(stringr)
```


# Introduction

You can and should cross-reference sections and sub-sections. 

The remainder of this paper is structured as follows. @sec-data....



# Data {#sec-data}

Our data is Marriage Licence Statistics from Open Data Toronto (citeopendatatoronto) which contains data sets maintained by the City of Toronto. The Marriage Licence Statistics dataset consists of monthly number of marriage licenses obtained from 2011 to 2023 in the Greater Toronto Area, it was last updated 2024-01-14. No similar data sets could have been used because this dataset is the only one of marriage licences.
```{r}
#| echo: false
marriage_data <- read_csv("outputs/data/cleaned_data.csv")

head(marriage_data)
```

The Marriage Licence Statistics dataset contains only four variables. _id is a unique identifier code given to each marriage license that is issued, we will not need it for our analysis so it is not selected during the data cleaning. CIVIC_CENTRE gives a two letter abbreviation of the city in which the marriage licenses are issued, ET for Etobicoke NY for North York, SC for Scarborough, and TO for Toronto. We will later examine each region separately. MARRIAGE_LICENSES is the variable denoting how many licenses were obtained each month, with a max of ----, min of ------, and average of -------. TIME_PERIOD is the month in which the marriage licenses were obtained in a yyyy-mm date format.



# Results

Our results are summarized in @tbl-modelresults.




# Discussion

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this. 

## Second discussion point

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix {-}


# Additional data details

# Model details {#sec-model-details}

## Posterior predictive check

In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...

In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows... 



\newpage


# References


